SoK: Transparent Dishonesty. Front-running attacks on Blockchain.

### 2018-12-05 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
\caption{ This chart shows the miners behaviour on the time window that Status.im ICO was running. It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network. \label{fig:Transactions_miners_while_status_ico_cut}} 
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
\caption{ F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses. On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract. Later on they sent the refunded Ether back to their own address. [Graph made using Blockseer.com] \label{fig:f2poolfront-run}}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{figures/solutions_mindmap.png}
\caption{ \emph{Solutions Mindmap}  \label{fig:solutions_mindmap.png}}
\end{figure}
%https://drive.mindmup.com/map/1u27BpAgU2CVy4BUf33cTRsOzJ01W3Gl2

@@

\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA), in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners. This is a theoretical solution and is not trivial to implement in the current Byzantine consensus protocols.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
\caption{ This chart shows the miners behaviour on the time window that Status.im ICO was running. It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network. \label{fig:Transactions_miners_while_status_ico_cut}} 
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.6\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
\caption{ F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses. On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract. Later on they sent the refunded Ether back to their own address. [Graph made using Blockseer.com] \label{fig:f2poolfront-run}}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/solutions_mindmap.png}
\caption{ \emph{Solutions Mindmap}  \label{fig:solutions_mindmap.png}}
\end{figure}
%https://drive.mindmup.com/map/1u27BpAgU2CVy4BUf33cTRsOzJ01W3Gl2

@@

\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA), in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners. This is a theoretical solution and is not trivial to implement in the current Byzantine consensus protocols. An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction hash~\cite{bitcoinABC2018CTOR}. This solution can potentially mitigate the re-ordering attack by miners, however it does not prevent it fully. 
%NOTE: the two solutions above are both on the transaction ordering, however Silva's solution requires a logical timestamp, and CTOR uses sorting based on transaction hash.
